---
title: "p8105_hw4_zx2231_tc2900_problem_1"
author: "Zenghui Xue"
date: "October 24, 2017"
output: html_document
---

**In Problem 1, Zenghui Xue (zx2231) leads and Shaoxuan Chen (tc2900) collaborates. **

```{r load_package, message=FALSE, echo = FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(haven)
library(dplyr)
library(janitor)
library(knitr)
library(DT)
library(ggridges)
```

####1.The following code chunk convert the pups data from "wide" format to "long" format, and shows the first six rows.
```{r wrangling, message = FALSE}
pups_data = (read_csv("./FAS_pups.csv", col_types = "ciiiii") %>%
  clean_names())
names(pups_data) = sub("pd_", "", names(pups_data))
pups_data = data.frame(pups_data %>%
  gather(key = pd_landmark, value = pd_outcome, ears:walk) %>%
  na.omit() %>%
  mutate(sex = recode(sex, `1` = "male", `2` = "female")))
head(pups_data)
```

```{r}
pups_data %>% 
  ggplot(aes(x= pd_outcome, y = pd_landmark, fill = pd_landmark)) +
  geom_density_ridges(scale = .77) +
labs(
    title = "Distribution of post-natal days for each developmental landmark",
    x = "Post-natal days",
    y = "Developmental landmark"
  ) + 
  theme(legend.position = "bottom")
```



* From the plot, we can see that the development of ears centralized in the 4th day, and the development of eyes centralized in the 13th day. The development of walk and pivot cluster between 8-12 days and 5-10 days, respectively.

* The reason of the distribution is that the development time of pups' body vary from parts to parts. But most of the pups development time close to each other.

























